Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-13 vesicle_code/docs/adhesion/adhesion.tex
added some new images and worked on extensional

\begin{figure}[htp]
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.03$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.
  After time $t=400$, the vesicles extensional rate has overcome the
  adhesive force, and the vesicles continue to separate.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width=0.45\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \todo[inline]{need a plot describing what the inclination angle
  is}
  \caption{\label{fig:extensionalInclinationAngle} The inclination angle
  of a doublet formed by vesicles of reduced area $0.70$ submerged in an
  extensional flow with an extensional rate of $\chi$.}
\end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.02$.
  The doublet tilts to an inclination angle.
  }
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.07$.
  The doublet tilts to an inclination angle.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.7$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.  The
  vesicles extensional rate has overcome the adhesive force, and the
  vesicles doublet is broken.}
\end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[height=0.4\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \hfill
  \includegraphics[height=0.4\textwidth]{figs/angleDefinition.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$. {\em Right}: The definition of the inclination angle.  An
  inclination angle of $\pi$ indicates a doublet whose long axis is
  parallel to the converging direction, while an inclination angle of
  $\pi/2$ indicates a doublet whose short axis is parallel to the
  converging direction.}
\end{figure}
